\documentclass[letterpaper,10pt]{article}
\usepackage[T1]{fontenc}
\usepackage{fontspec}
\usepackage{xltxtra}
\usepackage[letterpaper,margin=1.6cm,headheight=12pt]{geometry}
\usepackage{fancyhdr}
\usepackage{lastpage}
\usepackage{amsmath,amsthm,amsfonts,amssymb,amscd}
\usepackage{fontawesome5}
\usepackage{stix}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage[inline,shortlabels]{enumitem}
\usepackage{titlesec}
\usepackage{xifthen}
\usepackage[normalem]{ulem}
\usepackage{lipsum}
\usepackage[super]{nth}

\setmainfont{Noto Serif}

\definecolor{default}{HTML}{0064A4}

\hypersetup{
  colorlinks=true,
  linkcolor=black,
  urlcolor=default,
  linkbordercolor={0 0 1}
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{\baselineskip}
\renewcommand{\headrulewidth}{0pt}
\newcommand{\name}{M Badri Narayanan}

\fancyhf{}
\fancyfoot[L]{\footnotesize \name $\:$ Résumé}
\fancyfoot[R]{\footnotesize Page\ \thepage\ of\ \pageref{LastPage}}
\pagestyle{fancy}

\newcommand{\headlink}[3]{
    \normalsize#1\enspace\large\href{#2}{\texttt{#3}}
}

\fancypagestyle{firstpage}{
    \fancyhead[L]{}
    \fancyhead[R]{}
}

\AtBeginDocument{
    \thispagestyle{firstpage}
    \begin{center}
        \huge\textsc{\textbf{\name}} \par
        \large
        \begin{itemize*}[label={},afterlabel={},itemjoin={\enspace|\enspace}]
            \item \headlink{\faInternetExplorer}{https://mbadrinarayanan.github.io}{mbadrinarayanan.github.io}
            \item \headlink{\faGithub}{https://github.com/MBadriNarayanan}{MBadriNarayanan}
            \item \headlink{\faLinkedin}{https://www.linkedin.com/in/mbadrinarayanan}{mbadrinarayanan}
            \item \headlink{\faEnvelope}{mailto:immbadri3@gmail.com}{immbadri3@gmail.com}
        \end{itemize*}
    \end{center}
    \vspace{-8pt}
    \normalsize
}

\newenvironment{cvitemize}{
    \begin{itemize}[leftmargin=10pt,label={},afterlabel={},after=\vspace{-12pt}]
}{
    \end{itemize}
}

\newenvironment{cvenumerate}{
    \begin{enumerate}[leftmargin=20pt,after=\vspace{-12pt}]
}{
    \end{enumerate}
}

\titlespacing*{\section}{0pt}{0pt}{0pt}
\titlespacing*{\subsection}{0pt}{0pt}{-5pt}
\titleformat{\section}{\large\color{default}\scshape\bfseries}{\thesection}{1em}{}[{\color{black}\titlerule[0.2pt]}]
\titleformat{\subsection}{\bfseries}{\thesubsection}{1em}{\hspace{10pt}}[]

\newcommand{\eduitem}[5]{
    \item{
        \textbf{#1} \hfill \textit{#2} \newline
        \textit{#3} \hfill \textit{#4} \newline
        #5
    }
}

\newcommand{\point}{\raisebox{0.1\height}{$\rightarrow$}\hspace{4pt}}

\newcommand{\expitem}[6]{
    \item{
        \textbf{#1} \hfill \textit{#2} \newline
        \textit{#3} \hfill \textit{#4} \newline
        \point #5 \newline
        #6
    }
}
\renewcommand{\ULthickness}{0.2pt}
\newcommand{\me}{\uline{\name}}

\newcommand{\pubitem}[5]{
    \item{
        \textit{#1} \hfill #5 \newline
        #2 \newline
        \textit{#3}
        \ifthenelse{\isempty{#4}}
            {}
            {\newline #4}
    }
}

\begin{document}

\section*{Education}
\begin{cvitemize}
    \eduitem{SSN College of Engineering, Chennai}{Jun 2018 -- Jun 2022 (expected)}{B.Tech. Information Technology}{GPA: 8.60 / 10 }{
        \textbf{Courses:} Discrete Mathematics, Data Structures \& Algorithms\newline
        \textbf{Societies:} Coding Club
    }
    \eduitem{Vidya Mandir Senior Secondary School, Chennai}{Jun 2017 -- Jun 2018}{Grade 12}{94.4 \%}{
        \textbf{Group:} Computer Science \newline
    }
\end{cvitemize}
\section*{Skills}
\textbf{Programming Languages:} Python, C, C++, Java, R, \LaTeX, MASM, GNU Octave\newline
\textbf{Web Development:} HTML5, CSS3, JavaScript \newline
\textbf{Software \& Tools:} Git, TensorFlow, Keras, PyTorch, scikit, NLTK, spaCy, OpenCV

\section*{Experience}
\begin{cvitemize}
    \expitem{Solarillion Foundation}{2020 -- present}{UG Research Assistant}{Chennai, India}{Research on sign language translation.}{\textbf{Advisor:} Mr. Vineeth Vijayaraghavan}
    \expitem{Freelance Projects}{2020 -- present}{Freelancer.com}{Chennai, India}{Undertook projects via Freelancer.com.}{\href{https://www.freelancer.in/u/HalceyonAI}{FreeLancer.com Profile}}
    \expitem{Prodian Info Tech Pvt Ltd}{Jun 2020 -- Aug 2020}{Summer Intern}{Chennai, India}{Applying unsupervised ML Algorithms to get the top 5 features that affect a cricket match.}{\textbf{Advisor:} Mr. Vijay Karthik}
    \expitem{Appcilious Pvt Ltd}{Aug 2020 -- Sep 2020}{ML / AI Intern}{Banglore, India}{Developed a chat bot using modern NLP techniques and architectures.}{\textbf{Advisor:} Mr. Arpan Deb}
\end{cvitemize}

% \section*{Publications}
%\begin{cvitemize}
    %\pubitem{Paper title}{Author 1, \me, Author 3, Author 4, Author 5}{Conference and Year}{}{\faGithub \enspace \href{https://github.com/}{Code} \quad \faFile \enspace %\href{https://drive.google.com/file/}{Slides}}
% \end{cvitemize}

\section*{Selected Projects}
\begin{cvitemize}
    \item{
        \textbf{Clickbait Classification} \hfill \faGithub \enspace \href{https://github.com/MBadriNarayanan/ClickbaitClassification}{Code} \enspace \textit{2020} \newline
        Classifying clickbaits using modern NLP techniques and architecture.
    }
    \item{
        \textbf{Flight Delay Prediction} \hfill \faGithub \enspace \href{https://github.com/MBadriNarayanan/FlightDelayPrediction}{Code} \enspace \textit{2020} \newline
        Developed a two stage machine learning model to predict if flights will be delayed upon arrival and if so, the delay in minutes based on the weather data at departure.
    }
    \item{
        \textbf{Machine Translator} \hfill \faGithub \enspace \href{https://github.com/MBadriNarayanan/MachineTranslation}{Code} \enspace \textit{2020} \newline
        English to French neural machine translator built using Transformer architecture in NLP.
    }
    \item{
        \textbf{Object Detection using YOLO V3} \hfill \faGithub \enspace \href{https://github.com/MBadriNarayanan/ObjectDetectionUsingYOLOv3}{Code} \enspace \textit{2020} \newline
        Detection of objects using YOLO V3 Algorithm on a custom dataset.
    }
\end{cvitemize}

\newpage
\section*{Awards \& Honours}
\begin{cvitemize}
    \item \point Stood school 3rd in Chemistry in 12th standard.
    \item \point Won the 2nd best project in Computer Science in 12th standard.
\end{cvitemize}

\section*{Volunteering \& Responsibilities}
\begin{cvitemize}
    \item \point Volunteering with Chennai Volunteers to teach spoken English classes for Tamil medium students.
    \item \point Captained the school cricket team.
    \item \point Represented the college cricket team.
\end{cvitemize}

\end{document}
